How to Make a Proceedings Paper Submission

### 2020-09-23 docs/resources/CogSci_paper/paper.tex
last update

The objective of the experiment was this time to see if people's causal judgements are

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=8cm]{results_E2}
\end{center}
\caption{This is a figure.} 
\label{fig:4}
\end{figure}

>>>>

The objective of the experiment was this time to see which event is seen as the main cause in cases where R1 and I2 are located on the same sequence. In other words we wanted to test the hypothesis that the main cause is the event that initiates a continous sequence of changes over time. We wanted to test it with different types of networks including networks with loop of detectors that don't maintain their activation through time and see if the type of networks influence as well causal judgements.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=8cm]{results_E2}
\end{center}
\caption{This is a figure.} 
\label{fig:4}
\end{figure}
